What Makes Deep Network Representations Good for Visual Recognition?

### 2015-04-06 paper_for_review.tex
v1.2

% Include other packages here, before hyperref.
\usepackage[labelfont=bf, skip=5pt]{caption}
\captionsetup{labelsep=period}
\usepackage{footmisc}

@@

Representations of artificial neurons in deep neural networks have been demonstrated to be highly effective and robust for various visual recognition tasks~\cite{krizhevsky2012imagenet, sermanet2013overfeat, donahue2014decaf}.
Nevertheless, our understanding of them arguably remains limited.
In this paper, we address two important and practical questions: (1) why deep networks are better than shallow networks, and (2) among networks of the same depth, why certain networks are better than the others. Using methods which support characterizing both first-order and second-order properties of scalar and vector representations, we considered the case study of face pair matching and conducted a large-scale experiment. This experiment examined 200 randomly generated shallow and deep networks, with the results analyzed through a series of measures designed to quantify the differences in representations. 
We conclude though this principled analysis that deep representations are quantitatively better than shallow representations, and overall 71\% of the variance in the performance of deep networks can be explained with our measures, both of which are confirmed using statistical tests for the first time.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.40\textwidth]{Figs/e_fig7s_compact-crop.pdf} 
\end{center}
\caption{{\bf What makes a deep network good?}
In existing work, researchers have mostly tried to produce one ``best'' network architecture (\ie a hyperparameter set, either through manual tuning or automated hyperparameter search), which is subsequently evaluated on a particular benchmark. However, as exemplified in this figure, when considering a larger population of networks \cite{cox2011beyond}, it is not fully clear to us why in practice deep networks (\eg two or more levels) outperform shallow networks (\eg one-level), and why certain networks are better than the others, given their broad distribution of performance on a task like face pair matching for the LFW-a data set (shown above)~\cite{LFWTech, wolf2011effective}.
%However, it is not fully clear that in practice (1) why deep networks are better than shallow networks, and (2) among networks of the same depth, why certain networks are better than the others.
%As exemplified in the figure, deep (\ie two-level) networks not only on average outperform shallow (\ie one-level) networks \cite{cox2011beyond}, but also exhibit a wide range of performance differences on LFW-a face recognition \cite{LFWTech, wolf2011effective}.
} % (\eg optimal stimulus). %and (sometimes) characterized its properties
\label{fig:perf}
\end{figure}

@@

%first order, second order, flexibility
{\bf Existing work.} 
Given an artificial neural network $f$, the study of how $f$ represents a high dimensional stimulus\footnote{\expstimdim} ${\bf{x}} \in \mathbb{R}^N$ as a representation 
${\bf{r}} = f\left( {\bf{x}} \right)$ in existing work mainly focused on the first-order (\ie linear) characterization of $f$ --- the analysis of optimal stimuli, stimuli which lead to the strongest responses of given neurons.
For single-level convolutional networks using squared pooling, \ie $f({\bf{x}}) = \left\| {\bf{K}} \otimes {\bf{x}} \right\|_{F}$, the optimal stimulus was shown to be analytically approximable \cite{saxe2011random} using a Gabor-like filter, whether the convolution kernel $\bf{K}$ is structural or random.
For multi-level convolutional networks, the optimal stimuli of neurons from various depths were numerically approximated \cite{ngiam2010tiled, le2012building, zeiler2014visualizing, simonyan2013deep} to qualitatively show neurons in deeper layers are tuned to more complex visual patterns.
The generalized concept of optimal stimulus in considering groups of neurons can also be adopted to study the representations by inverting them \cite{mahendran2014understanding}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.35\textwidth]{Figs/methods.pdf} 
\end{center}
\caption{{\bf Representation characterization methods.}
On the spherical (\ie constant energy) constraint of the $N$ dimensional stimulus space, similar to previous work, the first-order property (\ie optimal stimulus $\hat{\bf{x}}$, as shown in the figure's center) of a representation $\bf{r}$ is first iteratively searched (as the evolution of light gray eclipses shown in the figure) and analyzed.
However, unlike most previous work, the second-order properties (\ie invariant path $\lbrace \bf{x}^{+}_{\delta} \rbrace$ as dashed red curve and selectivity path $\lbrace \bf{x}^{-}_{\delta} \rbrace$ as dashed blue curve) at distances $0.1\pi$ to $0.5\pi$ from the optimal stimulus are also searched and analyzed.
Additionally, these methods are capable of characterizing both scalar and vector representations, where the ``fitnesses'' to be optimized correspond to Eq.~\ref{eq:O1}, \ref{eq:I1}, \ref{eq:S1} and Eq.~\ref{eq:O2}, \ref{eq:I2}, \ref{eq:S2}, respectively.
In this example, the scalar representation (\ie response) of the given neuron is tuned to a $45^{\circ}$ Gabor filter and invariant to phase changes, but selective to orientation changes.
}
\label{fig:methods}
\end{figure}

@@

\newcommand{\expsettings}{In other words, 32 channels of filters in the top level's convolution layers, a simple setting with reasonable performance.
Following the terminology in recent work, shallow and deep neurons corresponded to \texttt{pool1} and \texttt{pool2} layers respectively.
Stimulus dimensionalities of the shallow and deep neurons {were} $N=121$ and $441$ (\ie spatially overlapping $11\times11$ and $21\times21$ receptive fields). % respectively
Other minor changes included: nonlinear activations all simplified to \emph{ReLU} \cite{krizhevsky2012imagenet} mode and normalizations all in subtractive mode.
Overall, the architectures were more similar to those in \cite{simonyan2014very}, except pooling operations can be \emph{average}, \emph{squared}, or \emph{max-like} in our case.
}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.70\textwidth]{Figs/pic1.pdf} 
\end{center}
\caption{{\bf Visualization of properties of shallow (A--D) and deep scalar representations (E--H).}
Color of the boarder of an image indicates the fitness of the representation (\ie response of the neuron) driven by the image, with color map following the definition in Fig.~\ref{fig:methods}.
A and E show the search trajectories of \emph{optimal stimuli} of all 32 neurons from the best performing shallow and best performing deep networks, respectively, where A.1 and E.1 show the initial $1/f$ random stimuli, A.5 and E.5 the resultant optimal stimuli, and A.2--4 and E.2--4 three intermediate steps corresponding to the three largest curvatures in the fitness histories.
B and F show the \emph{invariance paths} of shallow and deep neurons, starting from the corresponding optimal stimuli show in A.5 and E.5, moving from $0.1\pi$ (B.1 and F.1) to $0.5\pi$ (B.5 and F.5) away accordingly.
C and G show the \emph{selectivity paths} of shallow and deep neurons, with definitions following B and F.
D and H show the \emph{invariance subspaces} sampled $0.1\pi$ away from the optimal stimuli, with 5 out of 20 results randomly selected.
Comparatively, \emph{deep neurons show more complex and diverse representational properties} than shallow neurons do.
} % do visually
\label{fig:allrep}
\end{figure*}

\begin{figure}
\begin{center}
\includegraphics[width=0.35\textwidth]{Figs/e_fig3a_2-crop-nup-crop.pdf} 
\end{center}
\caption{{\bf Fitness-distance analyses of shallow (A) and deep scalar representations (B).}
Fitnesses of invariance (red dots, \ie $\left\lbrace f\left(\bf{x}^{+}_{\delta}\right) \right\rbrace$) and selectivity paths (blue dots, \ie $\left\lbrace f\left(\bf{x}^{-}_{\delta}\right) \right\rbrace$) of all 3,200 shallow and 3,200 deep neurons are shown for comparison\protect\footnotemark.
Although both types of neurons show invariance, shallow neurons do not posses selectivity, since their selectivity paths overlap with the dashed line, the zero-selectivity baseline.
In other words, \emph{only deep neurons are selective}.
} %, and random walks (green dots, \ie $\left\lbrace f\left({\bf{x}}^{R}_{\delta}\right) \right\rbrace$)
\label{fig:fda}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.35\textwidth]{Figs/e_fig23b-crop.pdf} 
\end{center}
\caption{{\bf Comparison of shallow and deep scalar representation measures.}
Representation measures from left to right are, optimal stimulus spectral complexity (OSSC), invariance path potential (INPP), selectivity path potential (SLPP), and invariance subspace capacity (INSC), in which data points from shallow networks (left distributions) and deep networks (right distributions) are shown side by side.
Sensitivity indexes ($d'$) between distributions are $1.63$, $0.42$, $4.73$, and $3.67$, respectively.
}
\label{fig:pair}
\end{figure}

@@

{\bf Overall comparison.} Comparisons of spectral complexities, invariance/selectivity path potentials, and invariance subspace capacities of shallow and deep neurons (as scalar representations) are summarized in Fig.~\ref{fig:pair}.
These measures further reveal the significant\footnote{\defstars} differences between shallow and deep representations, in addition to the separability and classifiability used in previous studies \cite{donahue2014decaf, zeiler2014visualizing}.
For instance, subtle differences of visual features have better chances being distinguished when the ``gap'' between invariance and selectivity curves (\ie the dynamic range of neuronal responses, or amplification ratio of differences) is large. 
The highly structural representations of neurons from deep networks with purely random convolution kernels found in the experiments also explain why such ``random'' deep networks can still have good performances, on top of the theoretical analysis for (one-level) shallow networks \cite{saxe2011random}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.70\textwidth]{Figs/pic2.pdf} 
\end{center}
\caption{{\bf Explanatory power of optimal stimuli of deep neurons.}
Results from deep networks of the top 3 strongest average explanatory power (A--C) and the weakest average explanatory power (D) are visualized.
Within each panel, the first row shows all 32 neurons' optimal stimuli from the network, the third to fifth rows show natural images with the top 3 strongest ``explainabilities'' (\ie inner-product distances between the images and the corresponding optimal stimuli), and the second row shows the average of images with top 100 explainabilities, out of 10,000 natural images.
Color of the boarder of an image indicates the explainability of the image, with color map following the definition in Fig.~\ref{fig:methods}.
Comparing deep networks' explanatory power and performances shows significant correlation (OSEP measure in Fig.~\ref{fig:corr}), which suggests \emph{``representing'' natural images can be required in first-order properties of good deep scalar representations (\ie optimal stimuli)}.
}
\label{fig:exppow}
\end{figure*}

\begin{figure}
\begin{center}
\includegraphics[width=0.35\textwidth]{Figs/pic3.pdf} 
\end{center}
\caption{{\bf Alignments of subspaces between invariance and selectivity paths and natural images.}
Using 16 natural images in A as reference stimuli, the invariance paths with $\delta = 0.1\pi$ corresponding to the best alignments against natural images (\ie $L^1$ sparsities of images represented in eigenface coordinates) among all deep networks are shown in B.1, and similarly, worst alignments of invariance paths in C.1, best alignments of selectivity paths in D.1, and worst alignments of selectivity paths in E.1.
Differences between A and B.1--E.1 are shown in B.2--E.2 for clearer visualization.
Color of the boarder of an image indicates the alignment of the image against natural images, with color map following the definition in Fig.~\ref{fig:methods}.
As good alignments (B.1 and C.1) appear more natural (like structural deformations or lighting changes), bad alignments are mostly meaningless noises.
Comparing deep networks' subspace alignment measures and performances shows significant correlations (ITSA/STSA measures in Fig.~\ref{fig:corr}), which suggest \emph{a resemblance to natural image distributions can be required in second-order properties of good deep vector representations (\ie invariance and selectivity subspaces)}.
} %of subspaces % which are known to be important factors in visual recognition % accordingly
%Multiple runs of invariance and selectivity path searches are executed to form samples of the subspaces.
\label{fig:align}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.35\textwidth]{Figs/pic4.pdf} 
\end{center}
\caption{{\bf Reconstructability of deep vector representations (\ie encoding specificities of natural images).}
Using 16 natural images in A as reference stimuli, 3 examples of reconstructions from all deep networks with the best, second best, third best and worst average reconstructed image quality (SSIM) are shown in B--E respectively.
Color of the boarder of an image indicates the SSIM score between the image and reference stimulus, with color map following the definition in Fig.~\ref{fig:methods}.
Though the reconstructions are in general of lower spatial frequencies, some of the better ones do capture the spatial structures of reference stimuli decently well (\eg stimulus 1, 5, \etc).
Comparing deep networks' encoding specificities and performances shows significant correlations (ITSA/STSA measures in Fig.~\ref{fig:corr}), which suggest \emph{providing specific (\ie non-confounding) encoding of natural images can be required in first-order properties of good deep vector representations}.
} % (reconstructed)
\label{fig:encspc}
\end{figure}

>>>>

% Include other packages here, before hyperref.
\usepackage[labelfont=bf, skip=3pt]{caption}
\captionsetup{labelsep=period}
\usepackage{footmisc}

@@

Representations of artificial neurons in deep neural networks have been demonstrated to be highly effective and robust for various visual recognition tasks~\cite{krizhevsky2012imagenet, sermanet2013overfeat, donahue2014decaf}.
Nevertheless, our understanding of them arguably remains limited.
In this paper, we address two important and practical questions: (1) why deep networks are better than shallow networks, and (2) among networks of the same depth, why certain networks are better than the others. Using methods which support characterizing both first-order and second-order properties of scalar and vector representations, we considered the case study of face pair matching and conducted a large-scale experiment. This experiment examined 200 randomly generated shallow and deep networks, with the results analyzed through a series of measures designed to quantify the differences in representations. 
We conclude through this principled analysis that deep representations are quantitatively better than shallow representations, and overall 71\% of the variance in the performance of deep networks can be explained with our measures, both of which are confirmed using statistical tests for the first time.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.90\columnwidth]{Figs/e_fig7s_compact-crop.pdf} 
\end{center}
\caption{{\bf What makes a deep network good?}
In existing work, researchers have mostly tried to produce one ``best'' network architecture (\ie a hyperparameter set, either through manual tuning or automated hyperparameter search), which is subsequently evaluated on a particular benchmark. However, as exemplified in this figure, when considering a larger population of networks \cite{cox2011beyond}, it is not fully clear to us why in practice deep networks (\eg two or more levels) outperform shallow networks (\eg one-level), and why certain networks are better than the others, given their broad distribution of performance on a task like face pair matching for the LFW-a data set (shown above)~\cite{LFWTech, wolf2011effective}.
%However, it is not fully clear that in practice (1) why deep networks are better than shallow networks, and (2) among networks of the same depth, why certain networks are better than the others.
%As exemplified in the figure, deep (\ie two-level) networks not only on average outperform shallow (\ie one-level) networks \cite{cox2011beyond}, but also exhibit a wide range of performance differences on LFW-a face recognition \cite{LFWTech, wolf2011effective}.
} % (\eg optimal stimulus). %and (sometimes) characterized its properties
\label{fig:perf}
\end{figure}

@@

%first order, second order, flexibility
{\bf Existing work.} 
Given an artificial neural network $f$, the study of how $f$ represents a high dimensional stimulus\footnote{\expstimdim} ${\bf{x}} \in \mathbb{R}^N$ as a representation 
${\bf{r}} = f\left( {\bf{x}} \right)$ in existing work mainly focused on the first-order (\ie linear) characterization of $f$---the analysis of optimal stimuli, stimuli which lead to the strongest responses of given neurons.
For single-level convolutional networks using squared pooling, \ie $f({\bf{x}}) = \left\| {\bf{K}} \otimes {\bf{x}} \right\|_{F}$, the optimal stimulus was shown to be analytically approximable \cite{saxe2011random} using a Gabor-like filter, whether the convolution kernel $\bf{K}$ is structural or random.
For multi-level convolutional networks, the optimal stimuli of neurons from various depths were numerically approximated \cite{ngiam2010tiled, le2012building, zeiler2014visualizing, simonyan2013deep} to qualitatively show neurons in deeper layers are tuned to more complex visual patterns.
The generalized concept of optimal stimulus in considering groups of neurons can also be adopted to study the representations by inverting them \cite{mahendran2014understanding}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{Figs/methods.jpg} 
\end{center}
\caption{{\bf Representation characterization methods.}
On the spherical (\ie constant energy) constraint of the $N$ dimensional stimulus space, similar to previous work, the first-order property (\ie optimal stimulus $\hat{\bf{x}}$) of a representation $\bf{r}$ is first iteratively searched (as the evolution of light gray eclipses) and analyzed.
However, unlike most previous work, the second-order properties (\ie invariant path $\lbrace \bf{x}^{+}_{\delta} \rbrace$ and selectivity path $\lbrace \bf{x}^{-}_{\delta} \rbrace$) at distances $0.1\pi$ to $0.5\pi$ from the optimal stimulus are also searched and analyzed.
Additionally, these methods are capable of characterizing both scalar and vector representations, where the ``fitnesses'' to be optimized correspond to Eq.~\ref{eq:O1}, \ref{eq:I1}, \ref{eq:S1} and Eq.~\ref{eq:O2}, \ref{eq:I2}, \ref{eq:S2}, respectively.
In this example, the scalar representation (\ie response) of the given neuron is tuned to a $45^{\circ}$ Gabor filter and invariant to phase changes, but selective to orientation changes.
}
\label{fig:methods}
\end{figure}

@@

\newcommand{\expsettings}{\Ie 32 channels of filters in the top level's convolution layers, a simple setting with reasonable performance.
Following the terminology in recent work, shallow and deep neurons corresponded to \texttt{pool1} and \texttt{pool2} layers respectively.
Stimulus dimensionalities of the shallow and deep neurons {were} $N=121$ and $441$ (\ie spatially overlapping $11\times11$ and $21\times21$ receptive fields). % respectively
Other minor changes included: nonlinear activations all simplified to \emph{ReLU} \cite{krizhevsky2012imagenet} mode and normalizations all in subtractive mode.
Overall, the architectures were more similar to those in \cite{simonyan2014very}, except pooling operations can be \emph{average}, \emph{squared}, or \emph{max-like} in our case.
}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.80\textwidth]{Figs/pic1.jpg} 
\end{center}
\caption{{\bf Visualization of properties of shallow (A--D) and deep scalar representations (E--H).}
Color of the boarder of an image indicates the fitness of the representation (\ie response of the neuron) driven by the image, with color map following the definition in Fig.~\ref{fig:methods}.
A and E show the search trajectories of \emph{optimal stimuli} of all 32 neurons from the best performing shallow and best performing deep networks, respectively, where A.1 and E.1 show the initial $1/f$ random stimuli, A.5 and E.5 the resultant optimal stimuli, and A.2--4 and E.2--4 three intermediate steps corresponding to the three largest curvatures in the fitness histories.
B and F show the \emph{invariance paths} of shallow and deep neurons, starting from the corresponding optimal stimuli show in A.5 and E.5, moving from $0.1\pi$ (B.1 and F.1) to $0.5\pi$ (B.5 and F.5) away accordingly.
C and G show the \emph{selectivity paths} of shallow and deep neurons, with definitions following B and F.
D and H show the \emph{invariance subspaces} sampled $0.1\pi$ away from the optimal stimuli, with 5 out of 20 results randomly selected.
Comparatively, \emph{deep neurons show more complex and diverse representational properties} than shallow neurons do.
} % do visually
\label{fig:allrep}
\end{figure*}

\begin{figure}
\begin{center}
\includegraphics[width=0.75\columnwidth]{Figs/fig4.pdf} 
\end{center}
\caption{{\bf Fitness-distance analyses of shallow (A) and deep scalar representations (B).}
Fitnesses of invariance (red dots, \ie $\left\lbrace f\left(\bf{x}^{+}_{\delta}\right) \right\rbrace$) and selectivity paths (blue dots, \ie $\left\lbrace f\left(\bf{x}^{-}_{\delta}\right) \right\rbrace$) of all 3,200 shallow and 3,200 deep neurons are shown for comparison\protect\footnotemark.
Although both types of neurons show invariance, shallow neurons do not posses selectivity, since their selectivity paths overlap with the zero-selectivity baseline.
In other words, \emph{only deep neurons are selective}.
} %, and random walks (green dots, \ie $\left\lbrace f\left({\bf{x}}^{R}_{\delta}\right) \right\rbrace$)
%the dashed line, 
\label{fig:fda}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.80\columnwidth]{Figs/fig5.pdf} 
\end{center}
\caption{{\bf Comparison of shallow and deep scalar representation measures.}
Representation measures from left to right are, optimal stimulus spectral complexity (OSSC), invariance path potential (INPP), selectivity path potential (SLPP), and invariance subspace capacity (INSC).
Sensitivity indexes ($d'$) between distributions are $1.63$, $0.42$, $4.73$, and $3.67$, and differences between means of distributions are all significant (***), which suggest \emph{deep representations are quantitatively and significantly better than shallow representations}.
} %, in which data points from shallow networks (left distributions) and deep networks (right distributions) are shown side by side
\label{fig:pair}
\end{figure}

@@

{\bf Overall comparison.} Comparisons of spectral complexities, invariance/selectivity path potentials, and invariance subspace capacities of shallow and deep neurons (as scalar representations) are summarized in Fig.~\ref{fig:pair}.
These measures further quantify the significant\footnote{\defstars} differences between shallow and deep representations, in addition to the separability and classifiability used in previous studies \cite{donahue2014decaf, zeiler2014visualizing}.
For instance, subtle differences of visual features have better chances being distinguished when the ``gap'' between invariance and selectivity curves (\ie the dynamic range of neuronal responses, or amplification ratio of differences) is large. 
The highly structural representations of neurons from deep networks with purely random convolution kernels found in the experiments also explain why such ``random'' deep networks can still have good performances, on top of the theoretical analysis for (one-level) shallow networks \cite{saxe2011random}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{Figs/pic2.jpg} 
\end{center}
\caption{{\bf Explanatory power of optimal stimuli of deep neurons.}
Results from deep networks of the top 3 strongest average explanatory power (A--C) and the weakest average explanatory power (D) are visualized.
Within each panel, the first row shows all 32 neurons' optimal stimuli from the network, the third to fifth rows show natural images with the top 3 strongest ``explainabilities'' (\ie inner-product distances between the images and the corresponding optimal stimuli), and the second row shows the average of images with top 100 explainabilities, out of 10,000 natural images.
Color of the boarder of an image indicates the explainability of the image, with color map following the definition in Fig.~\ref{fig:methods}.
Comparing deep networks' explanatory power and performances shows significant correlation (OSEP measure in Fig.~\ref{fig:corr}), which suggests \emph{``representing'' natural images can be required in first-order properties of good deep scalar representations (\ie optimal stimuli)}.
}
\label{fig:exppow}
\end{figure*}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth, trim=1em 0 1em 0]{Figs/pic3.jpg} 
\end{center}
\caption{{\bf Alignments of subspaces between invariance and selectivity paths and natural images.}
Using 16 natural images in A as reference stimuli, the invariance paths with $\delta = 0.1\pi$ corresponding to the best alignments against natural images (\ie $L^1$ sparsities of images represented in eigenface coordinates) among all deep networks are shown in B.1, and similarly, worst alignments of invariance paths in C.1, best alignments of selectivity paths in D.1, and worst alignments of selectivity paths in E.1.
Differences between A and B.1--E.1 are shown in B.2--E.2 for clearer visualization.
Color of the boarder of an image indicates the alignment of the image against natural images, with color map following the definition in Fig.~\ref{fig:methods}.
As good alignments (B.1 and C.1) appear more natural (like structural deformations or lighting changes), bad alignments are mostly meaningless noises.
Comparing deep networks' subspace alignment measures and performances shows significant correlations (ITSA/STSA measures in Fig.~\ref{fig:corr}), which suggest \emph{a resemblance to natural image distributions can be required in second-order properties of good deep vector representations (\ie invariance and selectivity subspaces)}.
} %of subspaces % which are known to be important factors in visual recognition % accordingly
%Multiple runs of invariance and selectivity path searches are executed to form samples of the subspaces.
\label{fig:align}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth, trim=1em 0 1em 0]{Figs/pic4.jpg} 
\end{center}
\caption{{\bf Reconstructability of deep vector representations (\ie encoding specificities of natural images).}
Using 16 natural images in A as reference stimuli, 3 examples of reconstructions from all deep networks with the best, second best, third best and worst average reconstructed image quality (SSIM) are shown in B--E respectively.
Color of the boarder of an image indicates the SSIM score between the image and reference stimulus, with color map following the definition in Fig.~\ref{fig:methods}.
Though the reconstructions are in general of lower spatial frequencies, some of the better ones do capture the spatial structures of reference stimuli decently well (\eg stimulus 1, 5, \etc).
Comparing deep networks' encoding specificities and performances shows significant correlations (ITSA/STSA measures in Fig.~\ref{fig:corr}), which suggest \emph{providing specific (\ie non-confounding) encoding of natural images can be required in first-order properties of good deep vector representations}.
} % (reconstructed)
\label{fig:encspc}
\end{figure}
